Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Move web services URLs to references

Google App Engine (\url{https://developers.google.com/appengine/})
is a web application platform.
Each application gets a user-specified subdomain of \urll{appspot.com},
which can be fronted through almost any Google domain,
including google.com, gmail.com, googleapis.com, and many others.
App Engine can run only web applications,
not a full Tor bridge;
for that reason we use a tiny ``reflector'' application
that merely copies incoming requests to a Tor bridge hosted elsewhere.
Fronting through App Engine is attractive in the case where
\urll{appspot.com} is blocked---not unlikely,
because of the ease of building a proxy there---but
at least one other Google service is reachable.
Applications that use less than one gigabyte of bandwidth daily
are free of charge,
making possible an upload-your-own-app model
à la GoAgent.

Amazon CloudFront (\url{https://aws.amazon.com/cloudfront/}),
not to be confused with CloudFlare,
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
an automatically generated subdomain of \urll{cloudfront.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other of CloudFront's automatically generated subdomains, all
of which support HTTPS through a wildcard certificate.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50 gigabytes per month.

CloudFlare (\url{https://www.cloudflare.com/}),
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

Akamai (\url{http://www.akamai.com/}) is a large CDN.
Requests may be fronted through the special HTTPS domain
\urll{a248.e.akamai.net},
which serves a certificate also good for \urll{*.akamaihd.net}.
The collateral damage of blocking Akamai is enormous:
in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
Akamai costs more than other CDNs;
it would likely require institutional support
to keep a circumvention system running on it in the long term.

Microsoft Azure (\url{http://azure.microsoft.com/})
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
There are other fronting domain names, like \urll{ajax.aspnetcdn.com},
that may offer high collateral damage.

Fastly (\url{http://www.fastly.com/}) is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
It is the only service we have found
that requires the ``domainless'' fronting style.

>>>>

Google App Engine~\cite{googleappengine}
is a web application platform.
Each application gets a user-specified subdomain of \urll{appspot.com},
which can be fronted through almost any Google domain,
including google.com, gmail.com, googleapis.com, and many others.
App Engine can run only web applications,
not a full Tor bridge;
for that reason we use a tiny ``reflector'' application
that merely copies incoming requests to a Tor bridge hosted elsewhere.
Fronting through App Engine is attractive in the case where
\urll{appspot.com} is blocked---not unlikely,
because of the ease of building a proxy there---but
at least one other Google service is reachable.
Applications that use less than one gigabyte of bandwidth daily
are free of charge,
making possible an upload-your-own-app model
à la GoAgent.

Amazon CloudFront~\cite{cloudfront},
not to be confused with CloudFlare,
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
an automatically generated subdomain of \urll{cloudfront.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other of CloudFront's automatically generated subdomains, all
of which support HTTPS through a wildcard certificate.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50 gigabytes per month.

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

Akamai~\cite{akamai-site} is a large CDN.
Requests may be fronted through the special HTTPS domain
\urll{a248.e.akamai.net},
which serves a certificate also good for \urll{*.akamaihd.net}.
The collateral damage of blocking Akamai is enormous:
in 2010 it carried 15--20\% of all web traffic~\cite{akamai}.
Akamai costs more than other CDNs;
it would likely require institutional support
to keep a circumvention system running on it in the long term.

Microsoft Azure~\cite{azure}
is a cloud computing platform that features a CDN.
Similarly to CloudFront, users get automatically generated subdomains
of \urll{vo.msecnd.net},
all of which can front for each other.
There are other fronting domain names, like \urll{ajax.aspnetcdn.com},
that may offer high collateral damage.

Fastly~\cite{fastly} is a CDN.
It is unique among the the services we tested in that
it is the only one that appears to enforce the SNI:
if the SNI and Host do not match,
the Fastly edge server returns an HTTP 400 (``Bad Request'') error.
However, if the TLS ClientHello omits SNI, then the Host may be any Fastly domain.
It is the only service we have found
that requires the ``domainless'' fronting style.
